\documentclass[a4paper]{article}

\usepackage{fullpage} % Package to use full page
\usepackage{parskip} % Package to tweak paragraph skipping
\usepackage{tikz} % Package for drawing
\usepackage{amsmath}
\usepackage{hyperref}

\title{CSCI 39548-03(4864) Web Development}
\author{Instructor: Jaime Canizales}
\date{Monday 5:30-8:00pm, Online-Synchronous, Fall 2024}

\begin{document}
\maketitle

\textbf{Textbook:} This is a zero cost course. All reading materials will be freely available to enrolled students.
\\ \\
\textbf{Email:} jaime.canizales@hunter.cuny.edu \\
\textbf{Office Hours:} By appointment.

\textbf{Learning Outcomes:} This course is an introduction to the fundamental concepts in web development. After completing this course, you will be able to build and deploy a website from scratch, as well as being able to understand, modify and contribute to the code of other websites. \\\\ 
\textbf{This course will cover the following topics:} 
\begin{enumerate}
    \item HTML
    \item Git
    \item CSS
    \item Javascript
    \item Document Object Model (DOM)
    \item Node Js
    \item Express and apis
    \item SQL (Postgressql)
    \item Docker
    \item React
\end{enumerate} 

\textbf{Grading: } \\
Midterm Exam: \hspace{1mm} 30\% \\
Final Exam: \hspace{6mm} 30\% (Scheduled by Hunter)\\
Homework: \hspace{8mm} 40\%

\textbf{Homeworks: } No late assignments will be accepted because we will go over the homework solution in class the day after its due. 

\textbf{Hunter College Official Policies:}\\
Hunter College regards acts of academic dishonesty (e.g., plagiarism, cheating on examinations, obtaining
unfair advantage, and falsification of records and official documents) as serious offenses against the values of
intellectual honesty. The college is committed to enforcing the CUNY policy on Academic Integrity and will
pursue cases of academic dishonesty according to the Hunter College Academic Integrity Procedures.
\par In compliance with the American Disability Act of 1990 (ADA) and with Section 504 of the Rehabilitation
Act of 1973, Hunter College is committed to ensuring educational parity and accommodations for all students
with documented disabilities and/or medical conditions. It is recommended that all students with documented
disabilities (Emotional, Medical, Physical and/or Learning) consult the Office of AccessABILITY located in
Room E1124 to secure necessary academic accommodations. For further information and assistance please call
(212-772-4857)/TTY (212-650-3230)\\\\
\par Bullying, cyberbullying, online hate, intimidation, threats, harassment, and pressure to share schoolwork
are all forms of violence. CUNY holds a zero tolerance stance towards all such acts. The University
is committed to prevention of any form of bullying, will respond promptly to threats and/or acts, and
will protect victims of bullying from retaliation. As a criminal matter, the New York Attorney General
defines cyberbullying as the use of email, websites, instant messaging, chat rooms, text messaging and
digital cameras to antagonize and intimidate others. Disrupting a teleconferencing platform (such as
Zoom/Skype/Blackboard Collaborate Ultra) is a federal crime.\\\\
\textbf{Hunter College Policy on Sexual Misconduct:}\\
In compliance with the CUNY Policy on Sexual Misconduct, Hunter College reaffirms the prohibition of
any sexual misconduct, which includes sexual violence, sexual harassment, and gender-based harassment
retaliation against students, employees, or visitors, as well as certain intimate relationships. Students
who have experienced any form of sexual violence on or off campus (including CUNY-sponsored trips and
events) are entitled to the rights outlined in the Bill of Rights for Hunter College. a. Sexual Violence:
Students are strongly encouraged to immediately report the incident by calling 911, contacting NYPD
Special Victims Division Hotline (646-610-7272) or their local police precinct, or contacting the College’s
Public Safety Office (212-772-4444). b. All Other Forms of Sexual Misconduct: Students are also encouraged to contact the College’s Title IX Campus Coordinator, Dean John Rose (jtrose@hunter.cuny.edu or
212-650-3262) or Colleen Barry (colleen.barry@hunter.cuny.edu or 212-772-4534) and seek complimentary
services through the Counseling and Wellness Services Office, Hunter East 1123. CUNY Policy on Sexual
Misconduct Link: http://www.cuny.edu/about/administration/offices/la/Policy-on-Sexual-Misconduct12-1-14-with-links.pdf

\end{document}